---
title: "Problem 2"
author: "Gloria and Adaeze"
format: pdf
editor: visual
---

# 2. Write a function that uses a for loop that, for each iteration, randomly draws 5 observations from an exponential distribution with “rate” parameter 1 (use rexp()) and calculates its “mean”. It should do this 10,000 times. Choose an appropriate plot to plot the distribution of “means

```{r}
si_means <- function() {
  means <- numeric(10000)
  for (i in 1:10000) {
    random_draw <- rexp(5, rate = 1)
    means[i] <- mean(random_draw)
  }
  
  return(means)
}

means <- si_means()

hist(means, main = "Distribution of Means from Exponential Distribution", xlab = "Mean", breaks = 30, col = "purple")
```

## 2a. Repeat part 1 by using a map\_\*() function.

```{r}
si_means_map <- function() {
  means <- map_dbl(1:10000, ~ mean(rexp(5, rate = 1)))
  return(means)
}
means_map <- si_means_map()

hist(means_map, main = "Distribution of Means from Exponential Distribution (map_dbl)", 
     xlab = "Mean", breaks = 30, col = "blue")
```

## 2b. Repeat part 1 by using the replicate() function

```{r}
si_means_replicate <- function() {
  means <- replicate(10000, mean(rexp(5, rate = 1)))
  return(means)
}
means_replicate <- si_means_replicate()

# Plot a histogram of the means with blue color
hist(means_replicate, main = "Distribution of Means from Exponential Distribution (replicate)", 
     xlab = "Mean", breaks = 30, col = "yellow")
```

## 2c. Use a another for loop that will print out plots for sample sizes of 5, 10, and 20 observations (instead of just 5)

```{r}
si_and_plot <- function() {
  sam_sizes <- c(5, 10, 20)
  for (n in sam_sizes) {
    means <- replicate(10000, mean(rexp(n, rate = 1)))
    
    hist(means, main = paste("Distribution of Means with Sample Size", n),
         xlab = "Mean", breaks = 30, col = "pink")
  }
}
si_and_plot()
```